\documentclass[10pt, a4paper]{extarticle}
\usepackage[footnotes,definitionLists,hashEnumerators,smartEllipses,hybrid,inlineFootnotes]{markdown}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{linkcolor=blue,urlcolor=blue,colorlinks=true}
\usepackage{microtype}
\usepackage{lmodern}
% Paragraph spacing
\usepackage[parfill=2pt]{parskip}
% Headings format
% List spacing
\usepackage{enumitem}
\usepackage{titlesec}
% Disable page number
\pagenumbering{gobble}


% Headings
\setcounter{secnumdepth}{0}
\titleformat*{\section}{\normalfont\large\bfseries}%\color{MidnightBlue}}
\titleformat*{\subsection}{\normalfont}%\color{MidnightBlue}}
% Headings spacing
\titlespacing\section{9pt}{7pt plus 1pt minus 1pt}{0pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{1pt plus 1pt minus 1pt}{1pt plus 1pt minus 1pt}
% List spacing
\setlist{nosep, leftmargin=*}
\setlist{parsep=0pt, topsep=0pt, itemsep=1pt, leftmargin=*}
% Title format
\makeatletter
\def\@maketitle{
  \newpage{\Large\textbf{{\@title}} } \\
 \hfill Paris, France | Italian and Dutch citizenship | \href{mailto:violettavanveen@gmail.com}{\texttt{violettavanveen@gmail.com} |  \url{https://violettavanveen.github.io}} 

\vspace{-4pt}

}
\makeatother
\title{Violetta van Veen}
\author{}

\begin{document}


\maketitle
\vspace{-0.8em}
\hrulefill


\hypertarget{education}{%
\section{Education}\label{education}}

\subsection{\textbf{Public Policy and Development}. Paris School of Economics
\textbar{} 2021-2023.}

\begin{itemize}
\item
  Master's in applied economics with an emphasis on econometrics and evaluation of public policies. Admission rate:
  \textless10\%
\item
  Selected coursework: Microeconomics, Econometrics: Treatment effect
  models, Measurement of policy outcomes.
\item
  Current GPA: 18.33/20.
\end{itemize}

\subsection{\textbf{Economics, Markets and Institutions.} University of Bologna
\textbar{} 2018-2021.}

\begin{itemize}
\item
  Graduated \textbf{summa cum laude} (equivalent to \emph{mention ``très
  bien''}). GPA: 29.83 out of 30.
\item
  Bachelor's in Economics, with emphasis on public policies. Selected
  coursework: Public Economics, Behavioral Economics, Labor Economics,
  Microeconomics, Macroeconomics, Economic History.
\item
  \textbf{Erasmus} Exchange at \textbf{Tilburg University} in fall 2020.
  Selected coursework: Econometrics, Philosophy of Free Markets, Policy
  Analysis in Public Administration.
\item
  Final project: ``Gender-based division of labor and fertility: from
  Becker (1960)'s theory to recent debates''
\end{itemize}

\subsection{\textbf{Collegio Superiore}. University of Bologna \textbar{} 2018-2021.}

\begin{itemize}
\item
  \textbf{Honors college}, which offers an additional education, with
  specialized seminars and interdisciplinary courses.
\item
  The admission is based on \textbf{merit}. Selected students
  (\textless5\% admission rate) are granted a full-ride scholarship,
  accommodation and the tutorship of a professor (in my case, Prof. S.
  Toso) as long as they meet a demanding GPA threshold in their degree
  program and Collegio Superiore's additional courses.
\item
  \textbf{TAship} for the seminar ``Equality and efficiency of taxation
  policies'' for my tutor, prof. S. Toso. Organized the final exam in
  form of a two-sided debate.
\item
  Organizer and founder of a competitive \textbf{debate} club. Each
  month, we organize a debate in which two teams of students debate the
  pros and cons of a socio-economic issue.
\end{itemize}

\hypertarget{work-experience}{%
\section{Work experience}\label{work-experience}}

\subsection{\textbf{Research Intern}. European Youth Think-Tank, Strasbourg
\textbar{} Spring 2021.}

\begin{itemize}
\item
  Wrote an \textbf{article} about the effects of Brexit and low
  productivity of Italy on the Blue Banana, the productive core of the
  European Union. Using R to process the Eurostat database, I produced
  comparative statistics for key variables at NUTS-2 levels. Currently
  \textbf{under review} at "History of Economic Thought and Policy" -
  Franco Angeli review.
\item
  Organized and moderated a conference on the Platform for the
  Conference on the Future of Europe on the topic of academic research
  in the post-pandemic era.
\item
  Gave a speech in a panel discussion organized by Institute for
  Knowledge Transfer (Berlin) about the economic impact of migration in
  terms of innovation.
\end{itemize}

\subsection{\textbf{Librarian Intern}. Fondazione Einaudi, Turin \textbar{}
2016-2017}

\begin{itemize}
\item
  Working on the bibliographical database of the Foundation's
  library, specialized in economics.
\end{itemize}

\subsection{\textbf{Italian teacher for foreign students}. Amici di Lazzaro, Turin
\textbar{} Summer 2019}

\vspace{3pt}\hypertarget{grants}{%
\section{Grants}\label{grants}}

\begin{itemize}
\item
  Current: Ermenegildo Zegna Founder's Scholarship for Talented Italian
  Students.
\end{itemize}

For my \textbf{Master's}, I was awarded grants for other universities,
but I have renounced to them to opt for PSE:

\begin{itemize}
\item
  Merit-based admission to the Erasmus Mundus Joint Master's Degree in
  Models and Methods of Quantitative Economics (QEM), full scholarship
  with paid tuition fees and monthly allowance
\item
  Merit-based admission in Economics Master's at University of Bologna,
  eligible for full scholarship
\end{itemize}

At \textbf{Bachelor's} level, I was awarded other full-ride
scholarships, but I have renounced to them to opt for the University of
Bologna:

\begin{itemize}
\item
  Merit-based admission to International College, University of Venice
  Ca' Foscari with a full-ride scholarship.
\item
  Merit-based admission to Carlo Alberto College (Turin)
\item
  Merit-based admission to Polytechnic of Turin's «Young talents»
  program.
\end{itemize}

\hypertarget{language-and-computer-skills}{%
\section{Language and computer
skills}\label{language-and-computer-skills}}

\begin{itemize}
\item
  \textbf{Italian}: mother tongue. \textbf{English}: upper C1 (IELTS,
  score 8 out of 9, January 2021). \textbf{French}: B1 (DELF, January
  2020)
\item
  Full command of R and RMarkdown, LaTeX, Microsoft Office and Google
  Suite. Data visualization and graphic design (Crello, Canva).
  Collaboration tools (Trello, When2Meet, Doodle).
\end{itemize}

\hypertarget{academic-projects}{%
\section{Academic Projects}\label{academic-projects}}

\begin{itemize}
\item
  Wrote a critical \textbf{replication} paper of Hatton
  (\href{https://www.aeaweb.org/articles?id=10.1257/aer.p20161062}{2016}),
  using R to replicate the econometric relations from the same database.
  Tilburg University \textbar{} 2020
\item
  As a student in \textbf{Collegio Superiore}, every year I wrote 5
  papers based on individual research on one of the topics addressed
  during the courses. Among others, ``The platformization of the
  Internet infrastructure: economic and social effects in cities''
  (\href{https://www.treccani.it/magazine/chiasmo/scienze_naturali_e_tecnologia/Pubblico_vs_privato/CSB_van_Veen_e_Frick_Piattaforme_e_servizi_Internet_nello_spazio_urbano_contemporaneo_seconda_parte.html}{published}
  on Treccani ``Il Chiasmo'' magazine), ``Equality of Opportunity and
  Gender Equality in Italian Excellence Colleges'' (1st place winner at
  ``Rete di Idee'' call for paper). \textbar{} 2018-2021
\end{itemize}


\end{document}

